Hybrid platforms and bargaining power

### 2024-05-26 src/paper/application.tex
Explain notation better

Imagine that there is a unit mass of consumers, looking to buy one product each.
They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
Customer $j$ derives the following utility from buying product $T_i$:
\begin{align*}
    u_{T_i}^j = v_{T_i} - p_{T_i} + \mu\epsilon_{T_i}^j \quad \text{for } T_i \in \{F, P\},
\end{align*}
where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product within its category is the same.
I.e., $v_{T_i} = v_T \, \forall\,i$.
This is to simplify the analysis, but is not crucial for the results.

@@

In practice, the resulting entry fees look as follows.
Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.

>>>>

Imagine that there is a unit mass of consumers, looking to buy one product each.
They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
Customer $j$ derives the following utility from buying product $T_i$\footnote{
    To avoid duplication, I denote the different types of products by $T_i$, where $T \in \{F, P, 0\}$ (fringe products, platform profucts, and outside options, respectively).
    This notation is used throughout the paper for other variables having fringe and platform counterparts, as well.
}:
\begin{align*}
    u_{T_i}^j = v_{T_i} - p_{T_i} + \mu\epsilon_{T_i}^j \quad \text{for } T_i \in \{F, P\},
\end{align*}
where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product within its category is the same.
I.e., $v_{T_i} = v_T \, \forall\,i$.
This is to simplify the analysis, but is not crucial for the results.

@@

In practice, the resulting entry fees look as follows.
Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.\footnote{
    Throughout this paper, I use the notation $\pi_T$ to denote the profits realized by player(s) $T$, and $\Pi$ to denote the total industry profits.
    Furthermore, $\pi^v_T$ denotes profits from sales (i.e., profits not including investment costs and entry fees), whereas $\pi^t_T$ stands for total profits.
}
